---
title: "Effect of statement complexity on mean 4C using ANOVA and Regression"
author: "David McMillan"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, echo=FALSE, cache=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = '..')
setwd("..")
options(width = 250)
load("C:/Users/David McMillan/Google Drive/PROJECTS/4C_QuantWritingAnalysis-in-R_featuredevelopment/Misc/instructionWorkspaces/instructions.RData")
```

This document will step through the process of creating a dataframe from the imported Master Excel Data Sheets (MEDS).  The created dataframe can then be used for subsequent analyses and testing hypotheses.

The process of creating the data frame break down to the following steps:

1. Opening the MEDS excel file and importing data.
2. Selecting a worksheet to form basis of dataframe
3. Adding additional columns of data from other worhsheets.
4. Saving data frame to disk to be used for analysis later.



1. The initial step to creating the dataframe consists of importing the MEDS file.  The import process is started with the following command:


This function creates 2 object in the R Environemnt, shown below:

A) importResults.frame, a dataframe containing a list of all the worksheets imported from excel.
```{r importResults.frame,eval=TRUE}
print(head(importResults.frame))
```
B) xlsData.FrameList, a list object with each element in the list containing a dataframe created from a single imported excel worksheet.
```{r, echo=FALSE}
getwd()
ls()
class(xlsData.FrameList)
names(xlsData.FrameList)
```
























Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).
